COG-ED Manuscript

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
effect sizes mlm 2nd

  # intraclass correlation (ICC)
  # % of variance can be explained by differences between persons
  var_m0_h2b <- as.data.frame(VarCorr(m0_h2b))
  icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2])

@@

To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) on the basis of the null model. <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ? Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist? -->
Second, we will estimate a random slopes model of SVs including *n*-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  -->

To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

>>>>

  # intraclass correlation (ICC)
  var_m0_h2b <- as.data.frame(VarCorr(m0_h2b))
  icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2])

  # get pseudo-r-squared -------------------------------------------------------

  ## for the whole model
  h2b_total_r2 <- r.squaredGLMM(m1_h2b, pj2014 = T)

  ## H2b: n-back level
  # according to https://doi.org/10.1186/s40536-018-0061-2 after Aiken and West 1991
  # model without effect
  m1_h2b_without <- lmer(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
                         data = h2b_data,
                         REML = T)
  # calculate R²
  h2b_without_r2 <- r.squaredGLMM(m1_h2b_without, pj2014 = T)

  # calculate f² with conditional R²
  h2b_r2 <- (h2b_total_r2[1,2] - h2b_without_r2[1,2]) / (1 - h2b_total_r2[1,2])

  ## H2c: NFC score
  m1_h2c_without <- lmer(sv ~ level.cwc + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
                         data = h2b_data,
                         REML = T)
  # calculate R²
  h2c_without_r2 <- r.squaredGLMM(m1_h2c_without, pj2014 = T)

  # calculate f² with conditional R²
  h2c_r2 <- (h2b_total_r2[1,2] - h2c_without_r2[1,2]) / (1 - h2b_total_r2[1,2])

@@

To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) as effect size measure for random effects. 
ICC displays the proportion of variance that is explained by differences between persons. <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ? Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist? --> 
<!--CK: Die Intraklassenkorrelation wird immer auf Grundlage des Nullmodells berechnet. Sie gibt an, wieviel der Gesamtvarianz auf Unterschiede zwischen den Personen zurückgeführt werden kann. Das Nullmodell zeigt, wie stark sich die einzelnen Ebene-2-Einheiten in ihrer mittleren Ausprägung auf der aV unterscheiden. Daher enthält es keine Prädiktoren. Ich habe den letzten Teil des Satzes "on the basis of the null model" rausgenommen, da er redundant ist. -->
<!--CK: werden wie Korrelationskoeffizienten interpretiert (https://doi.org/10.1186/s40536-018-0061-2), könnten wir im Ergebnisteil demnach in der Größe einschätzen --->
Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!--CK: please add https://doi.org/10.1186/s40536-018-0061-2 -->.
<!--CK: these are the corresponding values: h2b_total_r2, h2b_r2, h2c_r2 -->
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  --> 
<!--CK: habe ich jetzt ergänzt -->
To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
